---
title: "Logistic Regression"
author: "Adwesh Behera - 20025006"
date: "11 September 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem Statement
The Pima Indians Diabetes Binary Classification dataset contains all of the data of female   patients of the same age belonging to Pima Indian heritage. The data includes medical data, such as glucose and insulin levels, as well as lifestyle factors of the patients. The columns in the dataset are as follows:
Number of times pregnant
Plasma glucose concentration of 2 hours in an oral glucose tolerance test
Diastolic blood pressure (mm Hg)
Triceps skin fold thickness (mm)
2-hour serum insulin (mu U/ml)
Body mass index (weight in kg/(height in m)^2)
Diabetes pedigree function
Age (years)
Class variable (0 or 1)
The last column is the target variable or class variable that takes the value 0 or 1, where 1 is positive or affected by diabetes and 0 means that the patient is not affected.

You have to build models that could predict whether a patient has diabetes or tests positive or not using logistic regression

## Data

```{r, echo=TRUE}
rm(list = ls())
data = read.csv("Pima Indians Diabetes Binary Classification dataset.csv")
str(data)
```

## Division into Training and Test Datasets

We make take 100 rows as test cases and use the rest 668 as training data.

```{r, echo=TRUE}
sample_i = sample(768, 100)
data_train = data[-sample_i,]
data_test = data[sample_i,]
```


## Model

```{r, echo=TRUE}
model = glm(Class.variable..0.or.1. ~ ., data = data_train, family = binomial)
model
```

## Prediction

```{r, echo=TRUE}
predict = ifelse(predict(model, data_test,type = "response") > 0.5, 1, 0)
```

## Accuracy


```{r, echo=TRUE}
table(predict, data_test$Class.variable..0.or.1.)

error = mean(predict != data_test$Class.variable..0.or.1.)
accuracy = 1 - error

print(accuracy)
```